From Education To Entrepreneurship

### 2014-11-29 FromEducationToEntrepreneurship.Rmd
Clean Rmd
Cleaning

---
title: "From Education To Entrepreneurship"
author: "Thierry Racaud"
date: "29 novembre 2014"
output: html_document
---

@@

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "From Education To Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "29 novembre 2014"
output: html_document
---

@@

* * * 
```{r echo=FALSE, cache=TRUE, include=FALSE}

# Set working directory
setwd('~/Assign2Education/Proposal')

# Install necessary packages

# Install rempis from Christpher Gandrud's website
devtools::install_github('christophergandrud/repmis')
library(repmis)

# Load citation package
pkgs <- c('repmis')
repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')

```
